\documentclass[11pt,a4paper,calibri]{moderncv}

% modern themes
\moderncvstyle{banking}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[left=0.75in,right=0.75in,top=0.60in,bottom=0.30in]{geometry}
\usepackage{enumitem}
\usepackage{url}
\usepackage{hyperref} % Make sure to include hyperref package
\hypersetup{
    colorlinks=true, % Enable colored links
    linkcolor=blue,  % Color for internal links
    urlcolor=blue,   % Color for external links
    citecolor=blue,  % Color for citations
    pdfauthor={Aman Raj},
    pdftitle={Aman Raj's Resume},
}

\name{Aman}{Raj}
\email{amanraj11188@gmail.com}
\homepage{https://github.com/AmanGupta445052}  
\phone[mobile]{+91 8539995262}
\social[linkedin]{aman-gupta-545272226}

\begin{document}

\makecvtitle
\vspace{-35pt}

\small
\renewcommand\UrlFont{\color{blue}\rmfamily\underline} % Underline URLs

\section{Education}
\setlength\itemsep{.2em}
\cventry{June 2021 -- June 2025}{}{Kalinga Institute of Industrial Technology}{\textmd\textbf{Bhubaneswar, India}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
\vspace{-10pt}
\textit{B.Tech in Computer Science and Engineering }}

\cventry{2021}{}{Deoghar College}{\textmd\textbf{Deoghar, Jharkhand, India}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
\vspace{-10pt}
\textit{12th Class - Jharkhand Academic Council Board}}

\cventry{2019}{}{Dav Public School}{\textmd\textbf{Deoghar, Jharkhand, India}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
\vspace{-10pt}
\textit{10th Class - Central Board of Secondary Education (CBSE)}}

\section{Skills}
\begin{itemize}[leftmargin=.2in]
    \setlength\itemsep{.2em}
    \item \textbf{Programming Languages:} C/C++, JavaScript, Python, Java
    \item \textbf{Development:} HTML, CSS, Bootstrap, React, Node.js, Tailwind CSS, Express
    \item \textbf{Databases:} MongoDB, MySQL
    \item \textbf{Others:} Git, Linux, Firebase, Vercel
\end{itemize}

\section{Experience}
\begin{itemize}[leftmargin=0.0in]
    \setlength\itemsep{.2em}
    \vspace{-1pt}
    \cventry{Jan 2024 - May 2024}{}{Web Development Intern}{\textmd\textbf{RnPsoft PVT. LTD}}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.3em}
        \item Led the development and implementation of “RnPsoft 
              CodeHub,” a collaborative platform enabling employees
              to manage and update code for various software projects, enhancing team collaboration and code quality.
        \item Integrated version control features to track code changes, 
              allowing teams to maintain a history of project updates and revert changes as needed.
        \item Gained hands-on experience with modern web technologies, 
              including React, MongoDB, Javascript and Node.js.
        }
\end{itemize}

\section{Projects}
\begin{itemize}[leftmargin=0.0in]
    \setlength\itemsep{.2em}
    \cventry{July 2024}{Personalized Video Feed Platform}{{VidVerve} \textnormal{\textit{\href{https://github.com/AmanGupta445052/VidVerve}{\underline{GitHub}}}}}{}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.2em}
        \item Developed a personalized video feed platform, aggregating YouTube videos based on user preferences.
        \item Implemented a tag-based filtering system and personalized feed to enhance user engagement.
        \item Built using React, Node.js, MongoDB, Express, Tailwind CSS.
    }
    \cventry{October 2023}{Graph Algorithm Visualization Tool}{{Graph Project} \textnormal{\textit{\href{https://github.com/AmanGupta445052/Graph-Project}{\underline{GitHub}}}}}{}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.2em}
        \item Developed a comprehensive visualization tool for 
             pathfinding algorithms, offering interactive demonstrations
             of various algorithms.
        \item Implemented a suite of algorithms including Dijkstra’s, 
             A*, Greedy Best-first Search, Swarm, Convergent
             Swarm, Bidirectional Swarm, BFS, and DFS, showcasing their performance and use cases. Added a Recursive
            Division Maze Generation feature to enhance algorithm testing and visualization.
        \item Built using JavaScript, HTML, CSS, Express, Node.js, 
                   React.js.
    }
    \cventry{January 2024}{Personal Finance Tracker}{{Financial Tracker} \textnormal{\textit{\href{https://github.com/AmanGupta445052/Financial_Tracker}{\underline{GitHub}}}}}{}{}{ \setlength{\itemindent}{.2in} \setlength\itemsep{.2em}
        \item Developed a comprehensive Personal Finance Tracker for managing income, expenses, and financial goals.
        \item Built using React.js, Chart.js, Node.js, Express.js, MongoDB.
    }
\end{itemize}

\section{Certifications}
\cvitem{}{\href{https://www.hackerrank.com/certificates/e35a35918d8f}{\underline{\textbf{Problem Solving (Intermediate)}}} - Hackerrank}
\cvitem{}{\href{https://www.hackerrank.com/certificates/e35a35918d8f}{\underline{\textbf{SQL (Intermediate)}}} - Hackerrank}
\cvitem{}{\href{https://coursera.org/share/03f269c7ccf1222c1ffd3d8edf73c079}{\underline{\textbf{Generative AI: Introduction and Applications}}} - Coursera}
\cvitem{}{\href{https://coursera.org/share/c2e57b1df0c471d584db43bb16e49fb8}{\underline{\textbf{Prompt AI}}} - Coursera}

\vfill

\end{document}
